---
title: "Exploratory Data Analysis Project 1 Codebook"
author: "Michael G Harpole"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Plot 1

This plot is a histogram which shows the global active power in kilowats. Components of the histogram:

* color of the bins are red. 
* y axis label is frequency. 
* x axis label is Global Active Power (kilowats). 
* main title is Global Active Power

```{r, plot 1,warning=FALSE}
myFiles <- list.files(pattern="*.txt")
myFiles
myData <- read_delim(myFiles[1],na="?",show_col_types = FALSE) %>% 
  mutate(Date=lubridate::dmy(Date)) %>% 
  filter(between(Date, as.Date('2007-02-01'), as.Date('2007-02-02')))
# only want dates between 2007-02-01 and 2007-02-02
summary(myData)
head(myData)
names(myData)
hist(myData$Global_active_power,col = "red",
     xlab = "Global Active Power (kilowats)",
     main="Global Active Power")
dev.copy(png,"plot1.png")
dev.off()
```

# Plot 2
This plot is a line graph showing global active power across 3 days.
The graph componenets are:

* y label is Global Active Power (kilowats).
* x label is days of the week
* no main title

```{r plot2, warning=FALSE}
myFiles <- list.files(pattern="*.txt")
myFiles
myData <- read_delim(myFiles[1],na=c("?"),show_col_types = FALSE) %>% 
  mutate(Date=lubridate::dmy(Date)) %>% 
  filter(between(Date, as.Date('2007-02-01'), as.Date('2007-02-02'))) %>% 
  mutate(DateTime = lubridate::ymd_hms(paste(myData$Date,myData$Time)) )

plot(myData$DateTime,
     myData$Global_active_power,
     type = "l",
     xlab = "",
     ylab = "Global Active Power (kilowats)")
dev.copy(png,"plot2.png")
dev.off()
```

# Plot 3
This is a multivariable graph showing energy sub_meeting across time
Components of graph:

* y label Energy sub metering
* x no label
* black line with sub_metering_1
* red line with sub_metering_3
* blue line with sub_metering_3
* legend with three sub headings and corresponding colors
```{r plot3, warning=FALSE}
myData <- read_delim("household_power_consumption.txt",
                     na=c("?"),
                     show_col_types = FALSE) %>% 
  mutate(Date=lubridate::dmy(Date)) %>% 
  filter(between(Date, as.Date('2007-02-01'), as.Date('2007-02-02'))) %>% 
  mutate(DateTime = lubridate::ymd_hms(paste(myData$Date,myData$Time)) )

plot(myData$DateTime,
     myData$Sub_metering_1,
     type = "l",
     xlab = "",
     ylab = "Enerygy sub metering")
lines(myData$DateTime,
     myData$Sub_metering_2,
     col="red")
lines(myData$DateTime,
      myData$Sub_metering_3,
      col="blue")
legend("topright",
       lty = c(1,1,1),
       col = c("black","red","blue"),
       legend=c("Sub_metering_1","Sub_metering_2","Sub_metering_3"))
dev.copy(png,"plot3.png")
dev.off()
```

